A smart street lighting system based on \rev{an} IPv6-enabled wireless sensor network

### 2014-12-16 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex
mudança no algoritmo
algoritmo geoRank corrigido

The \textit{GeoRank} operation is depicted in Algoritm \ref{alg}.

Será que não é necessário algumas definições? (não sei, pq a maioria do que precisaria definir já é definido no protocolo RPL)
Existe o conceito de reliable nodes? (acredito que não)

O algoritmo do CDF completo foi colocado textualmente no artigo original. Será que cabe mesmo utilizar pseudo-code para descrevê-lo?

Consider a RPL network $G$ comprised of a set $S$ of nodes and a set $B$ of border routers (DODAGs root). We first introduce the concept of Rank and DODAG preferred parent.

@@

\begin{mydef}
DODAG Preferred Parent (DPP): Let $u$ be a node of $G$, $N(u)$ its one-hop neighbors and $DPP(u,j)$ a restricted subset of $N(u)$. For each node $v \in N(u)$, $v \in DDP(u,j)$ if it is a preferred parent for node $u$ next hop in order to reach a specific DODAG root $j \in B$. OBS.: Conceptually, the preferred parent is a single parent. However, it may be a set of multiple parents if those parents are equally preferred and have identical Rank.
\end{mydef}

\small
\begin{algorithm}
\begin{algorithmic}
\caption{GeoRank}
\label{alg}
\small
\STATE \textbf{Step 1} - Store in the packet the DODAG root with the smallest angle to the source-destination
line. 
\STATE \textbf{Step 2} - Start with greedy step of GOAFR until: (case I) finding a void node (i.e. a node where GOAFR would switch to face  routing (OAFR)) or (case II) delivering the packet. In case I, store the current position in the packet and go to step 3.
\STATE \textbf{Step 3} - If the destination node is closer to the DODAG root (stored in the packet) than the current node or the DODAG root is closer to the destination node than the current node, forward to the next hop in the DODAG towards the root (i.e. upward route). If neither condition is satisfied, go to step 4. Whenever the current node position is closer to destination than the position stored in the packet in step 2, go to step 1.
\STATE \textbf{Step 4} -  Execute face routing mode of GOAFR until delivering the packet or returning to step 1.
\small
\end{algorithmic}
\end{algorithm}
\normalsize

>>>>

In order to better describe the entire proposed algorithm it is important to define the main principles in which it is based. Therefore, considering a RPL network $G$ comprised of a set $S$ of nodes and a set $B$ of border routers (DODAGs root), we describe the concept of Rank, DODAG preferred parent and DODAG root list.

%Será que não é necessário algumas definições? (não sei, pq a maioria do que precisaria definir já é definido no protocolo RPL). Existe o conceito de reliable nodes? (acredito que não)

%O algoritmo do CDF completo foi colocado textualmente no artigo original. Será que cabe mesmo utilizar pseudo-code para descrevê-lo?

@@

\begin{mydef}
DODAG Preferred Parent (DPP): Let $u$ be a node of $G$, $N(u)$ its one-hop neighbors and $DPP(u,j)$ a restricted subset of $N(u)$. For each node $v \in N(u)$, $v \in DDP(u,j)$ if it has the lowest rank to reach a specific DODAG root $j \in B$.
\end{mydef}

OBS.: Conceptually, the preferred parent is a single parent. However, it may be a set of multiple parents if those parents are equally preferred and have identical Rank.

\begin{mydef}
DODAG Root List (DRL): each node $v \in N(u)$ should broadcast DIO messages regularly, as previously described. For GeoRank operation, the position of the DODAGs root should be included in such messages. So, let $DRL(j)$ be a list of the DODAGs root position stored in each node $u$ of the network.
\end{mydef}

It is important to note that the proposed algorithm is only intended for down routes. The up routes should use the traditional RPL protocol. Therefore, based on the above definitions, the overall procedure of the \textit{GeoRank} operation is described in Algorithm \ref{alg}.

\small
\begin{algorithm}
\begin{algorithmic}
\caption{GeoRank}
\label{alg}
\small

\STATE \textbf{1. Initialize the algorithm:} Based on the DRL and, the positions of source and destination nodes, trace a line between the source and destination nodes. After, trace lines between the source node and each of the DODAGs root available in the DRL. The DODAG root $j \in DRL$ that has the smallest absolute angle difference to the source-destination line is chosen as a anchor node for the P2P communication. Such anchor node will only be used if the greedy forwarding portion of the GOAFR algorithm fails to deliver the packet. Finally, store the position of the chosen DODAG root $j \in B$ in the packet being forwarded. The angle calculation is better described in \citep{Denardin2011}.

\vspace{2.5mm}

\STATE \textbf{2. Greedy forwarding mode:} If there are one or more neighbors in $N(u)$ closer to the destination than the current node holding the packet $u$, forward the packet to the neighbor $v \in N(u)$ with the greater progress towards the destination. Repeat this approach while such condition exists. If there are no neighbor in such position, store the node $u$ position in the packet and switch to GeoRank mode.
%the info of the algorithm change and

\vspace{2.5mm}

\STATE \textbf{3. GeoRank mode:} If the destination node is closer to the anchor node $j$ (stored in the packet being routed) than the current node holding the packet $u$, forward the packet to the DODAG Preferred Parent $v \in DDP(u,j)$. Repeat such process until : \textbf{a)} the packet reaches a node $u$ whose position is closer to the destination than the position stored in the packet at step 2; \textbf{b)} the packet reach the DODAG root $j$; \textbf{c)} the packet reach the destination node. If condition ``a'' is met, go back to step 2. If condition ``b'' or ``c'' is satisfied, go to step 4.

\vspace{2.5mm}

\STATE \textbf{4. Face routing mode:} Execute face routing mode of GOAFR until: \textbf{a)} delivery the packet; \textbf{b)} the packet reaches a node $u$ whose position is closer to the destination than the position stored in the packet at step 2. If so, go back to step 2.

\small
\end{algorithmic}
\end{algorithm}
\normalsize
